A statistical analysis on factors that contributed/slowed down the spread of COVID-19

### 2020-10-26 Discussion/Presentation.tex
PUB

\documentclass{beamer}

\usepackage[utf8]{inputenc}

\usetheme{Madrid}
\usecolortheme{beaver}
%Information to be included in the title page:

@@

@@

\begin{columns}
\frametitle{Cluster features}
\column{0.3\textwidth}
\textbf{Provices (IT)}
\begin{itemize}
\item Unemployment '19
\item Private Transport '12 
\item Air Quality '19
\item Public Transport '12
\item Density '19
\item Mean income '19
\end{itemize}
\column{0.3\textwidth}
\textbf{Regions (IT)}
\begin{itemize}
\item Mortality
\item Pop. for GP
\item Mean Income '19
\item Number of Visits for Pop. '17
\item Public Transport 
\item Density '19
\item Mean income '19
\item Tests 
\item LEA '17
\item Number of visit '17
\item Public structures '17
\end{itemize}
\column{0.3\textwidth}
\textbf{Countries}
\begin{itemize}
\item PM$_{2.5}$ '16
\item Traffic Mortality '16
\item Pollution Mortality '16
\item GDP pro-capita '19
\item Health expenditure '17
\item UHC '17
\end{itemize}
\end{columns}
\end{frame}

@@

>>>>

\documentclass[compress]{beamer}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{varwidth}

\useoutertheme{miniframes}

\usetheme[progressbar=frametitle]{Madrid}
\usefonttheme{professionalfonts}
\setbeamertemplate{itemize items}[triangle]
\setbeamertemplate{enumerate items}[default]
\usecolortheme{beaver}

%Information to be included in the title page:

@@

\section{Intro}

@@

\section{Data}

\begin{frame}
\frametitle{Cluster features}
\begin{columns}
\column{0.3\textwidth}
\textbf{Provices (IT)}
\begin{itemize}
\item Unemployment '19
\item Private Transport '12 
\item Air Quality '19
\item Public Transport '12
\item Density '19
\item Mean income '19
\end{itemize}
\column{0.3\textwidth}
\textbf{Regions (IT)}
\begin{itemize}
\item Mortality
\item Pop. for GP
\item Mean Income '19
\item Number of Visits for Pop. '17
\item Public Transport 
\item Density '19
\item Mean income '19
\item Tests 
\item LEA '17
\item Number of visit '17
\item Public structures '17
\end{itemize}
\column{0.3\textwidth}
\textbf{Countries}
\begin{itemize}
\item PM$_{2.5}$ '16
\item Traffic Mortality '16
\item Pollution Mortality '16
\item GDP pro-capita '19
\item Health expenditure '17
\item UHC '17
\end{itemize}
\end{columns}
\end{frame}

@@

\begin{frame}
\frametitle{Provinces}

\begin{figure}[H]
\centering
\begin{minipage}{.6\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/Province_FULL_CorrMatrix.pdf}
\end{minipage}%
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=\linewidth,]{Pic/Province_FULL_Variances.pdf}
\end{minipage}
\end{figure}
\end{frame}

\frametitle{Provinces}

\begin{figure}[H]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/Province_FULL_Variables-PCA.pdf}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth,]{Pic/Provinces_PCA_FULL.pdf}
\end{minipage}
\end{figure}

\frametitle{Provinces}

\begin{columns}
\column{0.5\textwidth}
\begin{figure}[H]
\centering
\begin{minipage}{\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/Province_FULL_Variables-PCA.pdf}
\end{minipage}%
\end{figure}
\column{0.5\textwidth}
\begin{itemize}
\item The public transport, the density, the normalized cumulative cases and the mean income are positively correlated
\item This can be explained by the fact that a higher density, a higher public transport demand and a higher income increase the rate of contact between the individuals
\item Rich people can spend more money for social events or perhaps in to travels thus they increase their connectivity (the opposite happens for the unemployment)
\end{itemize}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Regions}

\begin{figure}[H]
\centering
\begin{minipage}{.6\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/Regions_CorrMatrix.pdf}
\end{minipage}%
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=\linewidth,]{Pic/Region_variances.pdf}
\end{minipage}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Regions}

\begin{figure}[H]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/Regioni_PCA_loadings.pdf}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth,]{Pic/Regions_FULL_PCA.pdf}
\end{minipage}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Countries}
\begin{figure}[H]
\centering
\begin{minipage}{.6\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/CorrMatrix_WORLD.pdf}
\end{minipage}%
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=\linewidth,]{Pic/Variances-PCA_WORLD.pdf}
\end{minipage}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Countries}
\begin{figure}[H]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth, ]{Pic/PCA-Loadings_WORLD.pdf}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth,]{Pic/World_FULLPCA.pdf}
\end{minipage}
\end{figure}
\end{frame}
